Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2019-04-25 review_response/review_response.tex

\rcomment{
Problem complexity. Though the exponential lower bound works, the given example seems excessively degenerate. It works only by assuming that all rectangles have identical area---otherwise, the ``smallest area must aggregate'' severely limits the options. Can the construction be altered to show an exponential lower bound where all regions have unique sizes? (or under some other assumption that is more realistic).

Complementing this paragraph, I'm also wondering if anything is known about whether the specific problem considered here is NP-hard?  
}

\textbf{Response}
We have improved our proof of the exponential lower bound.
In the new proof, all the rectangles have unique sizes;
see Section 3.3 (Exponential Lower Bound).
We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

\rcomment{
Compactness. 
Two models for compactness are given, one being linear and the other not. 
The motivation for needing the linear model is clear, 
but how different are these models? 
Is there any literature that already describes the correlation between these? 
Otherwise, I feel that the paper could be enriched 
by considering the correlation between the two in this setting 
(how well does \Astar-$g_2$ perform in terms of \Astar-$g_1$ / 
does it give similar quality when measuring~$g_2$-results using~$g_1$, 
or something like that). 
(Assuming you have the data/solutions, this would be comparatively easy to do?)
}

@@

\textbf{Response} Figure 5 shows some ideas of \textcite{Cheng2006}.
We agree with the reviewer that
options (b) and (c, d, e) cannot be applicable simultaneously.
Still, we think that the figure is useful to exemplify possible choices.
We have added the reference of \textcite{Cheng2006} into the caption.

\rcomment{Section 3.1. Is there a specific reason why the metric considers only the change between two levels? It seems that, unless the resulting patch is immediately part of another aggregation, the choice made has a longer lasting effect. In other words, in all subsequent maps, the choice causes some ``error'' in the intermediate map, yet this is only measured once.
}

\textbf{Response}
A reason is that we want to make the changes small 
so that users can follow maps easily.
We have added this argument in Section 1 (Introduction).

\rcomment{Fig. 24 -- the problem is attributed to the small shared boundary. But is this not ``simply'' an issue of compactness? (That is, the compactness is not weighted heavily enough / or not captured adequately?).
}
\textbf{Response} 
This is an interesting question.
According to our experiences, 
the weight factor that we applied defines a reasonable trade-off 
between the different conflicting objectives, 
when considering a solution as a whole. 
However, we are far from claiming that 
the applied weight factor has been optimally chosen. 
This would probably require a user study, 
which would be beyond the scope of our article.
We have added a corresponding argument into Section 9.2
(Using costs of type change and length).

### 2019-04-25 area_agg_seq_tsas.tex
improved according to Jan's feedback about reviewer 1 comment 11

\begin{table*}[tb]
\caption{A comparison of the greedy algorithm and \Astar		
	when using cost function~$g_1$ (see \eq\ref{eq:g_1}).
	For \Astar, we used two settings, 
	i.e.,~$W=200{,}000$ and~$W=400{,}000$.
	%
	Column~\#OS shows the numbers of regions 
    that we obtained optimal solutions.   
	%
	Column~\#FS presents 
    the numbers and the percentages of regions (out of~$N=734$) 
    that we obtained feasible (non-optimal) solutions.
	%
	Variable~$k_\mathrm{sum}$ is 
	the total number of repetitions.
	%
	Columns~\#nodes and~\#arcs are the total 
	numbers of nodes and arcs that \Astar visited  
	(for instances where we needed overestimation, 
	only the final attempt was counted).
	%
	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
	and~$\sum g_1$
	respectively denotes the sums of~$g_\mathrm{type}(\Pgoal)$,
	$g_\mathrm{comp}(\Pgoal)$, and~$g_1(\Pgoal)$ 
	over all the~$734$ instances 
	(see \eqs\ref{eq:g_type}, \ref{eq:g_comp}, 
	and~\ref{eq:g_1}).
	%
	The percentage in the \emph{Time}
	column is the fraction of the runtime 
    spent on solving the instances
	that we obtained feasible solutions.
    For \Astar, the time needed for overestimation
    is included.
}
\label{tab:AreaAgg_CaseStudy1_Statistics}
\centering
\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
\setlength{\tabcolsep}{0.7ex}
\begin{tabular}{lRRRCCCCCd{3.7}}
\toprule
\multicolumn{1}{l}{Methods} &
\multicolumn{1}{l}{\#OS} &
\multicolumn{1}{c}{\#FS} &
\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
\multicolumn{1}{c}{\#nodes} & 
\multicolumn{1}{c}{\#arcs} & 
\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
\multicolumn{1}{c}{$\sum g_\mathrm{comp}$} & 
\multicolumn{1}{c}{$\sum g_1$} & 
\multicolumn{1}{c}{Time (min)} \\ 
\midrule
Greedy 	& 408 
&326~(44.4\%) 
&             &5.5\cdot 10^3   &4.8\cdot 10^3   
&53.2         &188.2           &120.7           &0'1~(74.6\%)\\
%
%
\AstarTwo	& 702 
&  32~(\parbox{\widthof{$4$}}{$\,$}$4.4\%$) 
& 102 &  3.6\cdot 10^6 &    5.7\cdot 10^6	
& 51.4 & 183.2 & 117.3 & 51'6~(93.2\%)\\
%
%
\AstarFour	& 704 
&  30~(\parbox{\widthof{$4$}}{$\,$}$4.1\%$)
&  89 &  6.5\cdot 10^6 &    9.8\cdot 10^6
& 51.4 & 183.1 & 117.2 & 93'1~(95.5\%)
\\ \bottomrule			
\end{tabular}
\end{table*}

@@

\begin{table*}[tb]
\caption{A comparison of the greedy algorithm, 
    the \Astar algorithm, and the ILP-based algorithm		
	when using cost function~$g_2$ (see \eq\ref{eq:g_2}).
	The notations are the same as in
	\tab\ref{tab:AreaAgg_CaseStudy1_Statistics}.
	%
	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{lgth}$, 
	and~$\sum g_2$
	respectively represent the sums of~$g_\mathrm{type}(\Pgoal)$,
	$g_\mathrm{lgth}(\Pgoal)$, and~$g_2(\Pgoal)$ 
	over all the~$734$ instances 
	(see \eqs\ref{eq:g_type}, \ref{eq:g_length}, 
	and~\ref{eq:g_2}).
}
\label{tab:AreaAgg_CaseStudy2_Statistics}
%	\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
\centering
\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
\setlength{\tabcolsep}{0.7ex}
\begin{tabular}{lRRRCCCCCd{3.7}}
\toprule
\multicolumn{1}{l}{Methods} &
\multicolumn{1}{l}{\#OS} &
\multicolumn{1}{c}{\#FS} &
\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
\multicolumn{1}{c}{\#nodes} & 
\multicolumn{1}{c}{\#arcs} & 
\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
\multicolumn{1}{c}{$\sum g_\mathrm{lgth}$} & 
\multicolumn{1}{c}{$\sum g_2$} & 
\multicolumn{1}{c}{Time (min)} \\ 
\midrule
Greedy 		 &430             
&304~(41.4\%)    
&            &5.5\cdot 10^3   &4.8\cdot 10^3   
&53.0        &858.5           &455.8           &0'1~(70.7\%)\\
%
%
\AstarTwo	& 695
& 39~(\parbox{\widthof{$4$}}{$\,$}$5.3\%$)	
& 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 
& 52.0 	& 824.5 & 438.2 &44'8~(92.3\%)	\\
%
%
\ILPOne		& 449
& 69~(\parbox{\widthof{$4$}}{$\,$}$9.4\%$)  			 	
&		&				&				
&		&		&		& 421'5~(27.3\%) \\
%
%
\ILPTwo		& 475
& 57~(\parbox{\widthof{$4$}}{$\,$}$7.8\%$)  			 	
&		&				&				
&		&		&		& 719'2~(26.4\%) \\ 
\bottomrule
\end{tabular}
\end{table*}

@@

Among all the instances that were solved to optimality by \Astar
in both experiments (i.e., \sects\ref{sec:AreaAgg_CaseStudy1} 
and~\ref{sec:AreaAgg_CaseStudy2}),
region~$358$ (marked in \tab\ref{tab:CostsInDetail})
is the largest one.
In both experiments, the cost of type change is~$0.044$.
The optimal aggregation sequences for this region
obtained by using costs~$g_1$ and~$g_2$
are shown in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}.
We, however, noticed some unpleasant aggregates.
The step from~$8$ patches to~$7$ patches 
when using cost function~$g_1$ is a bad move
(see \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b).
Instead we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}a.
Using cost function~$g_2$, we had a similar problem. 
The subdivision with~$7$ patches is such an example,
where we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
In an earlier version of this paper \parencite{Peng2017AStar},
we tried a combination of minimizing type changes 
and maximizing the sum of the smallest compactness values, 
over the whole sequence.
For that objective, we had a similar problem as 
in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b.
This problem, however, can be fixed easily 
by forbidding two patches to aggregate 
if their common boundary is too short.

>>>>

\begin{table*}[tb]
\caption{A comparison of the greedy algorithm and \Astar		
	when using cost function~$g_1$ (see \eq\ref{eq:g_1}).
	For \Astar, we used two settings, 
	i.e.,~$W=200{,}000$ and~$W=400{,}000$.
	%
	Column~\#OS shows the numbers of regions 
    that we obtained optimal solutions.   
	%
	Column~\#FS presents 
    the numbers and the percentages of regions (out of~$N=734$) 
    that we obtained feasible (non-optimal) solutions.
	%
	Variable~$k_\mathrm{sum}$ is 
	the total number of repetitions.
	%
	Columns~\#nodes and~\#arcs are the total 
	numbers of nodes and arcs that \Astar visited  
	(for instances where we needed overestimation, 
	only the final attempt was counted).
	%
	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
	and~$\sum g_1$
	respectively denotes the sums of~$g_\mathrm{type}(\Pgoal)$,
	$g_\mathrm{comp}(\Pgoal)$, and~$g_1(\Pgoal)$ 
	over all the~$734$ instances 
	(see \eqs\ref{eq:g_type}, \ref{eq:g_comp}, 
	and~\ref{eq:g_1}).
	%
	The percentage in the \emph{Time}
	column is the fraction of the runtime 
    spent on solving the instances
	that we obtained feasible solutions.
    For \Astar, the time needed for overestimation
    is included.
}
\label{tab:AreaAgg_CaseStudy1_Statistics}
\centering
\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
\setlength{\tabcolsep}{0.7ex}
\begin{tabular}{lRRRCCCCCd{3.7}}
\toprule
\multicolumn{1}{l}{Methods} &
\multicolumn{1}{c}{\#OS} &
\multicolumn{1}{c}{\#FS} &
\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
\multicolumn{1}{c}{\#nodes} & 
\multicolumn{1}{c}{\#arcs} & 
\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
\multicolumn{1}{c}{$\sum g_\mathrm{comp}$} & 
\multicolumn{1}{c}{$\sum g_1$} & 
\multicolumn{1}{c}{Time (min)} \\ 
\midrule
Greedy 	& 408 
&326~(44.4\%) 
&             &5.5\cdot 10^3   &4.8\cdot 10^3   
&53.2         &188.2           &120.7           &0'1~(74.6\%)\\
%
%
\AstarTwo	& 702 
&  32~(\parbox{\widthof{$4$}}{$\,$}$4.4\%$) 
& 102 &  3.6\cdot 10^6 &    5.7\cdot 10^6	
& 51.4 & 183.2 & 117.3 & 51'6~(93.2\%)\\
%
%
\AstarFour	& 704 
&  30~(\parbox{\widthof{$4$}}{$\,$}$4.1\%$)
&  89 &  6.5\cdot 10^6 &    9.8\cdot 10^6
& 51.4 & 183.1 & 117.2 & 93'1~(95.5\%)
\\ \bottomrule			
\end{tabular}
\end{table*}

@@

\begin{table*}[tb]
\caption{A comparison of the greedy algorithm, 
    the \Astar algorithm, and the ILP-based algorithm		
	when using cost function~$g_2$ (see \eq\ref{eq:g_2}).
	The notations are the same as in
	\tab\ref{tab:AreaAgg_CaseStudy1_Statistics}.
	%
	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{lgth}$, 
	and~$\sum g_2$
	respectively represent the sums of~$g_\mathrm{type}(\Pgoal)$,
	$g_\mathrm{lgth}(\Pgoal)$, and~$g_2(\Pgoal)$ 
	over all the~$734$ instances 
	(see \eqs\ref{eq:g_type}, \ref{eq:g_length}, 
	and~\ref{eq:g_2}).
}
\label{tab:AreaAgg_CaseStudy2_Statistics}
%	\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
\centering
\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
\setlength{\tabcolsep}{0.7ex}
\begin{tabular}{lRRRCCCCCd{3.7}}
\toprule
\multicolumn{1}{l}{Methods} &
\multicolumn{1}{c}{\#OS} &
\multicolumn{1}{c}{\#FS} &
\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
\multicolumn{1}{c}{\#nodes} & 
\multicolumn{1}{c}{\#arcs} & 
\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
\multicolumn{1}{c}{$\sum g_\mathrm{lgth}$} & 
\multicolumn{1}{c}{$\sum g_2$} & 
\multicolumn{1}{c}{Time (min)} \\ 
\midrule
Greedy 		 &430             
&304~(41.4\%)    
&            &5.5\cdot 10^3   &4.8\cdot 10^3   
&53.0        &858.5           &455.8           &0'1~(70.7\%)\\
%
%
\AstarTwo	& 695
& 39~(\parbox{\widthof{$4$}}{$\,$}$5.3\%$)	
& 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 
& 52.0 	& 824.5 & 438.2 &44'8~(92.3\%)	\\
%
%
\ILPOne		& 449
& 69~(\parbox{\widthof{$4$}}{$\,$}$9.4\%$)  			 	
&		&				&				
&		&		&		& 421'5~(27.3\%) \\
%
%
\ILPTwo		& 475
& 57~(\parbox{\widthof{$4$}}{$\,$}$7.8\%$)  			 	
&		&				&				
&		&		&		& 719'2~(26.4\%) \\ 
\bottomrule
\end{tabular}
\end{table*}

@@

Among all the instances that were solved to optimality by \Astar
in both experiments (i.e., \sects\ref{sec:AreaAgg_CaseStudy1} 
and~\ref{sec:AreaAgg_CaseStudy2}),
region~$358$ (marked in \tab\ref{tab:CostsInDetail})
is the largest one.
In both experiments, the cost of type change is~$0.044$.
The optimal aggregation sequences for this region
obtained by using costs~$g_1$ and~$g_2$
are shown in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}.
We, however, noticed some unpleasant aggregates.
The step from~$8$ patches to~$7$ patches 
when using cost function~$g_1$ is a bad move
(see \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b).
Instead we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}a.
Using cost function~$g_2$, we had a similar problem. 
The subdivision with~$7$ patches is such an example,
where we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
In an earlier version of this paper \parencite[see][]{Peng2017AStar},
we tried a combination of minimizing type changes 
and maximizing the sum of the smallest compactness values, 
over the whole sequence.
For that objective, we had a similar problem as 
in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b.
This problem, however, can be fixed easily 
by forbidding two patches to aggregate 
if their common boundary is too short.
Moreover, there are two more possible solutions.
First, we could integrate the shared length
into our cost function, as did by \textcite{vanOosterom1995Development}.
Second, we could weight the cost of shape more heavily
(i.e., increasing weight factor~$\lambda$ of \eqs\ref{eq:g_1} and~\ref{eq:g_2}).
According to our experiences, 
the weight factor that we applied defines a reasonable trade-off 
between the different conflicting objectives, 
when considering a solution as a whole. 
However, we are far from claiming that 
the applied weight factor has been optimally chosen. 
This would probably require a user study.
